Notebook of learning from ensemble labels

### 2021-05-07 docs/notebook_learn_dl_ensemble.Rmd
Update dataset class

@@

- Learning rate and learning rate scheduler
- Batch size
- Transform methods (if necessary)

>>>>

#### Tensorboard

If download log file to local machine, then it is easy to check the training loss curves.

`tensorboard --logdir='./tensorboard_dirs' --port=16007`

Do the following steps to use the tensorboard on a remote server (reference: https://blog.yyliu.net/remote-tensorboard/):

1. You need to start SSH with transfer the remote server’s port to your local PC:

    (on your local PC) `ssh -L 16007:127.0.0.1:16007 username@server_ip`

2. Then you may start the tensorboard on the remote server with the specific port we want to transfer:

    (on the remote server) `tensorboard --logdir='./tensorboard_dirs' --port=16007`

@@

- Learning rate and learning rate scheduler
- Batch size
- Optimizer
- Model (Unet or Deeplab)
- Transform methods (if necessary)

#### Tuning plans

- Unet

  - Batch size = 32 (Maximum value fit into `g4dn.12xlarge`)
  - Initial learning rate = [0.1, 0.01, 0.001]

    - 0.1 is too large
    - 0.01 and 0.001 works similarly.

  - Optimizer: we plan to try some more recent optimizer such as AdaBound, AdamP, AdamW, etc. Because SGD could make model have higher generalization while Adam can train the model faster. So if we could use an optimizer that has both advantages, it would be ideal. Since our research is not about the improvement of DL algorithm, so we just pick up the most right one at the moment.

  - Scheduler: 0 - 50 use 0.01, 50 - 150 use a decayed cyclic scheduler (0.01 - 0.001), last 50: 0.001 with a tiny cycle range.
